\label{key}% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textheight}{9.5in} % increase text height to fit on 1-page 

\begin{document} 

\name{EVAN STOLL\\[12pt]}     % the \\[12pt] adds a blank
				        % line after name      

\address{estoll@asu.edu\\(480) 338-2918}

                                  
\begin{resume}
 
\section{EDUCATION}
\vspace{0.05in}          
    Arizona State University, Tempe, AZ  \\        
    Bachelor of Science, Computer Science, May 2016(Expected)   \\Dean's List       

 
\section{PROJECTS}
   \vspace{0.05in}	
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Saccadous Portal} \>Saccadous Inc.     \>Jan 2015-Dec 2015\\
   \end{tabbing}\vspace{-30pt}      % suppress blank line after tabbing
    Worked on a small team to help develop a cloud-based solution for patient data storage/retrieval and visualization.
    
    -Utilized Ruby on Rails to build an application that handled client data uploads and downloads.
    -Implemented user authentication system allowing users to create an account and login on the portal.
    -Gained experience working with the Microsoft Azure cloud platform.
    
    
    \begin{tabbing}
    	\hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    	{\bf Sorting Algorithm Visualizer}     \>\>Jan 2016\\
    \end{tabbing}
    \vspace{-30pt}      % suppress blank line after tabbing
    GitHub URL: https://github.com/estoll/VisuSort
    \\A Java program that allows users to see the work that various sorting algorithms do on randomly generated data.
    
    -Utilized Java2D to render the visual representation of the data being sorted.
    \\-Simple Swing GUI allows users to select sorting options(sorting algorithm, input size, step delay).
    \\-Aided in a deeper understanding of various sorting algorithms.
    
    \section{SKILLS}
    \vspace{0.05in} 
    \begin{tabbing}  
    	\hspace{2.3in}\= \hspace{2.6in}\= \kill       
    \bf Proficient:
    \>Java, C/C++, MySQL
    \\\bf Experience With:
    \>HTML, CSS, Ruby
    \\\bf Version Control:
    \>Git
	\end{tabbing}
    
    \section{EXPERIENCE}
    \vspace{0.05in}	
    \begin{tabbing}
    	\hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    	{\bf Operations Assistant} \>Saguaro Lake Ranch     \>Fall 2014-Present\\
    	\>Mesa, AZ
    \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    -Worked on a small team to provide our guests with the best experience possible.
    \\-Perform ground maintenance year round.
    \\-Assist in preparing and serving food for the guests.
    \\-Provide orientations and safety instructions on how to properly kayak.
    \\-Launch and transport kayaks along the Salt River.
           
    \begin{tabbing}
    	\hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    	{\bf Server/Busser} \>Broadway Palm Dinner Theater     
    	\>Fall 2008-Spring 2015
    	\\
    	\>Mesa, AZ
    \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    -Worked on a large team that provided customer service in a fast paced environment.
    \\-Delivered food and drinks in a timely manner.
    \\-Gain experience in working with customers and meeting their needs.
    \\-Promoted from busser to server during my employment, 
    
    \begin{tabbing}
    	\hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    	{\bf Maintenance Worker, Grounds} \>Haydon Building Corp     \>Summer 2013-Spring 2014\\
    	\>Phoenix, AZ
    \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    -Assisted in installing plumbing and electrical used for irrigation.
    \\-Prepared job sites for cement laying and general construction.    
  
 
\end{resume}
\end{document}
